My title

### 2024-11-04 paper/paper.qmd
Updated

library(tidyverse)
# library(palmerpenguins)
```

@@

The summary statistics below outline key variables in our analysis, focusing on Kamala Harris and Donald Trump. These tables display the distribution of support percentages and sample sizes, with metrics including mean, median, standard deviation, minimum, and maximum.

Table 1: Directly compares support percentages and sample sizes for Harris and Trump, showing central tendencies and variability in polling data for each candidate.

Table 2: Summarizes all numeric variables, providing a broader context on data variability, particularly in pollster reliability scores, support percentages, and sample sizes.

>>>>

library(tidyverse)
library(testthat)
library(arrow)
library(here)
library(rstanarm)
library(bayesplot)
library(gt)
library(kableExtra)

analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))
```

@@

The summary statistics below @SummaryStatisticsComparison outline key variables in our analysis, focusing on Kamala Harris and Donald Trump. These tables display the distribution of support percentages and sample sizes, with metrics including mean, median, standard deviation, minimum, and maximum.

```{r}
#| echo: false
#| warning: false
#| message: false
#| warning: false
#| label: SummaryStatisticsComparison
#| tbl-cap: Directly compares support percentages and sample sizes for Harris and Trump, showing central tendencies and variability in polling data for each candidate.

# Filter data for Harris and Trump
harris_data <- analysis_data %>%
  filter(candidate == "Kamala Harris")

trump_data <- analysis_data %>%
  filter(candidate == "Donald Trump")

# Define a function to compute summary statistics
compute_summary_stats <- function(data) {
  data %>%
    summarise(
      Mean = mean(percentage, na.rm = TRUE),
      Median = median(percentage, na.rm = TRUE),
      SD = sd(percentage, na.rm = TRUE),
      Min = min(percentage, na.rm = TRUE),
      Max = max(percentage, na.rm = TRUE),
      Sample_Size_Mean = mean(sample_size, na.rm = TRUE),
      Sample_Size_SD = sd(sample_size, na.rm = TRUE)
    )
}

# Summary statistics for Harris
harris_summary <- compute_summary_stats(harris_data) %>%
  mutate(Candidate = "Kamala Harris")

# Summary statistics for Trump
trump_summary <- compute_summary_stats(trump_data) %>%
  mutate(Candidate = "Donald Trump")

# Combine the two tables and format values to 2 decimal places
summary_table <- bind_rows(harris_summary, trump_summary) %>%
  select(Candidate, everything()) %>%
  mutate(across(where(is.numeric), ~ round(.x, 2)))  # Round numeric columns to 2 decimal places

# Rename columns in the summary table
summary_table <- summary_table %>%
  rename(
    `Sample Size Mean` = Sample_Size_Mean,
    `Sample Size SD` = Sample_Size_SD
  )

# Create a visual table using kable
summary_table %>%
  kable("html", caption = "Summary Statistics for Key Variables Comparing Kamala Harris and Donald Trump") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, position = "center") %>%
  add_header_above(c(" " = 1, "Percentage Statistics" = 5, "Sample Size Statistics" = 2)) %>%
  column_spec(2:8, width = "2em")  # Adjust column width if necessary

```
